SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-09-15 README.Rmd
JVS minor revision

# Sylvan Seeds

*Sylvan Seeds* is a database of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere. It contains data on >300 plant species, obtained from >600 published references. The data is in the form of germination proportions recorded under experimental combinations of temperature, light, scarification and stratification.

@@

@@

* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* The article describing the collection and fields of the database, which is in preparation.

>>>>

![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)

# SylvanSeeds, a seed germination database for temperate deciduous forests

This repository stores all the information related to the publication *SylvanSeeds, a seed germination database for temperate deciduous forests*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

*SylvanSeeds* is a dataset of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere. It contains data on >300 plant species, obtained from >500 published references. The data is in the form of germination proportions recorded under experimental combinations of temperature, light, scarification and stratification.

@@

This repository is organised following the advice of [Wilson et al. 2017](https://doi.org/10.1371/journal.pcbi.1005510) for recording and storing research projects.

@@

* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.
* [The database itself in `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The SylvanSeeds `shiny` app for visualizing the dataset](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* [The report paper describing the collection and fields of the dataset](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md), published in the Journal of Vegetation Science.

## Citation

Please cite the dataset as

> Fernández-Pascual, E (2020) SylvanSeeds, a seed germination database for temperate deciduous forests. Journal of Vegetation Science, in press.

### 2020-09-15 doc/manuscript.Rmd
JVS minor revision

Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope. This article presents *SylvanSeeds*, a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests. Data were gathered with a systematic literature search. A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database. The list was searched in the Web of Science. 6,791 references were screened, finding 614 articles from which data were extracted. *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017. It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures. *SylvanSeeds* is freely distributed as a *.csv*. The shiny app *SylvanSeeds* (https://efernandezpascual.shinyapps.io/sylvanseeds/) is also presented, to make data accessible to the public. *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.  First, the data-gathering methodology can be extended to other biomes. Second, database and app can be a standard in further efforts to compile germination data.

**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate broadleaf and mixed forests, temperate evergreen forests

@@

## Species list

A list of species for which to search germination data was created using vegetation relevés (i.e. records of plant species co-occurring in sampling plots) from *sPlot* [@RN4658]. The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates. To ensure that plots were a representative sample of nemoral biome biodiversity, they were chosen from 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome distributed throughout the northern hemisphere: (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*). Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684]. For this reason, they were not considered. For reasons unrelated to the deciduous forest search, three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*) were included in the search, and their species were searched for in parallel. For completeness, data from these three regions is also included with the database, but the records from the coniferous forest species are identified so they can be excluded at will (see below).

All chosen relevés had been classified as forest plots by *sPlot*, i.e. their plant cover was dominated by tree species. The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* version 3.6.2 [@RN2315]. The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers. To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species. There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of the nemoral biome, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.). The result is a list of plant species that occur with relatively high frequency in forest plots of the nemoral biome; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.

@@

The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)”. This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results. The processing of these results is described in a PRISMA flow diagram (**Supporting Information 1**). A first filter of the results by the relevance of the title retained 1,489 references. An effort was made to access the full text of all these references, using the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised. The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 2**) in case they can be processed in the future. The found texts were accessed to retrieve data for the database. At this stage, references were considered to be non-relevant if they (i) did not pertain to species in the original frequent species list; (ii) did not study germination in species monocultures (e.g. competition studies); (iii) did not report the minimal information needed (number of seeds sown, germination percentage and germination temperature). Records were also excluded when they pertained to special germination treatments that do not allow for general comparisons (i.e. use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins). Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 3**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 4**).

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**), in both hemispheres. Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere. These records are included in the database, and their geographical origin is reported. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Biome* (whether the species belongs to temperate broadleaf and mixed foresta [TBMF] or to the temperate coniferous biome [TCF]), *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

**Supporting Information 1** PRISMA 2009 flow chart describing the process of reference screening and inclusion. **Supporting Information 2** BibTeX bibliography listing the not found full texts.  **Supporting Information 3** BibTeX bibliography listing the non-relevant references.  **Supporting Information 4** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.  **Supporting Information 5** *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Supporting Information of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).

>>>>

Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope. This article presents *SylvanSeeds*, a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests. Data were gathered with a systematic literature search. A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database. The list was searched in the Web of Science. 6,791 references were screened, finding 555 articles from which data were extracted. *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017. It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures. *SylvanSeeds* is freely distributed as a *.csv*. The shiny app *SylvanSeeds* (https://efernandezpascual.shinyapps.io/sylvanseeds/) is also presented, to make data accessible to the public. *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.  First, the data-gathering methodology can be extended to other biomes. Second, database and app can be a standard in further efforts to compile germination data.

**Keywords:** germination database, germination temperature, light and dark germination, nemoral, seed dormancy, seed traits, temperate broadleaf and mixed forests, temperate evergreen forests

@@

## Frequent species list

A systematic approach was followed to search for data, with the purpose of prioritising work and maximising its utility for vegetation science. In short, this approach consisted in (i) obtaining a representative number of vegetation plots for the biome from sPlot (https://www.idiv.de/en/splot.html); and (ii) using the plots to produce a list of frequent species (i.e. species that occur in at least 5 % of the plots of a region).

A list of species for which to search germination data was created using vegetation relevés (i.e. records of plant species co-occurring in sampling plots) from *sPlot* [@RN4658]. The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates. To ensure that plots were a representative sample of nemoral biome biodiversity, they were chosen from 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome distributed throughout the northern hemisphere: (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*). Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684]. For this reason, they were not considered.

All chosen relevés had been classified as forest plots by *sPlot*, i.e. their plant cover was dominated by tree species. The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* [@RN2315]. The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers. To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species. There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of the nemoral biome, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.). The result is a list of plant species that occur with relatively high frequency in forest plots of the nemoral biome; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.

@@

The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)”. This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results. The processing of these results is described in a PRISMA flow diagram (**Appendix S1**). A first filter of the results by the relevance of the title retained 1,489 references. An effort was made to access the full text of all these references, using the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised. The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Appendix S2**) in case they can be processed in the future. The found texts were accessed to retrieve data for the database. At this stage, references were considered to be non-relevant if they (i) did not pertain to species in the original frequent species list; (ii) did not study germination in species monocultures (e.g. competition studies); (iii) did not report the minimal information needed (number of seeds sown, germination percentage and germination temperature). Records were also excluded when they pertained to special germination treatments that do not allow for general comparisons (i.e. use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins). Of the accessed references, 698 were non-relevant (*BiBTeX* file in **Appendix S3**) and 555 provided relevant data (*BiBTeX* file in **Appendix S4**).

The systematic approach applied may fail to capture references on species belonging to the nemoral biome for three reasons: (1) the species is not recorded in the vegetation database; (2) the species has been recorded, but it is infrequent (see above the frequency criterion); or (3) the species is recorded and frequent and goes into the list, but the relevant germination references are not found by the web search because the species name is not mentioned in the title or the abstract. While points 1 and 2 are intentionally excluded by the applied methodology, point 3 would be a failure of the methodology (specifically, a failure of the search string to find a relevant paper). For this reason, a protocol was applied to detect the importance of point 3, using the book of Baskin and Baskin [-@RN3214] as a reference. After completing the database, species names in the frequent species list for which no relevant papers had been found were searched in the taxonomical index of the Baskin and Baskin book. There were 273 species with missing data and mentioned by Baskin and Baskin in their index. A random sample of 10 % of these species were selected, and their references as mentioned in the book were searched. All of them were found to be either inaccessible (national journals or old conference proceedings not available online) or to have no relevant data (i.e. provided no primary germination data that could be retrieved). From this trial, it was concluded that the search string had found a reasonable amount of the available information, by comparing it to the best reference available, the review book of Baskin and Baskin.

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 555 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**), in both hemispheres. Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere. These records are included in the database, and their geographical origin is reported. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Appendix S5** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

**Appendix S1** PRISMA 2009 flow chart describing the process of reference screening and inclusion. **Appendix S2** Bibliography in BibTeX format listing the not-found full texts.  **Appendix S3** Bibliography in BibTeX format listing the non-relevant references.  **Appendix S4** Bibliography in BibTeX format listing the relevant references included in the *SylvanSeeds* database.  **Appendix S5** *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Appendix S5 of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).
